The binary liquid model for gravity-driven microchannel simulations

### 2010-11-04 Text/paper.tex
Finalized additional results.

\subsection{The influence of the wall gradient}
The results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$. This
section is to examine the wall gradient influence on simulations. We take large
enough resolution for simulations to be consistent. Simulation domain was
chosen as $177\mathrm{x}2626$ and the initial film width as
$12$ lattice boltzmann units, which correspond to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
$0.0633$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0633$,$0.0632$,
$0.0631$. The results are different in 4th digit. For the wall gradients $0.8$
and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles} The negative values of the phase gradient are
preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$ and do not interact
with the bubble which has phase value $-1$.  In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see if the width
is properly resolved then the wettability of the wall doesn't play any role
affecting the film thickness.
\label{fig:gradients:profiles}
}
\end{figure}

@@

\subsection{The film variation over the bubble}
Though this section

>>>>

\subsection{The influence of the wall gradient}
The results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$. This
section is to examine the wall gradient influence on simulations. We take large
enough resolution for simulations to be consistent. Simulation domain was
chosen as $177\mathrm{x}2626$ and the initial film width as
$12$ lattice boltzmann units, which correspond to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
$0.0633$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0633$,$0.0632$,
$0.0631$. The results are different in 4th digit. For the wall gradients $0.8$
and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles} The negative values of the phase gradient are
preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$ and do not interact
with the bubble which has phase value $-1$.  In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see if the width
is properly resolved then the wettability of the wall doesn't play any role
affecting the film thickness.
\label{fig:gradients:profiles}
}
\end{figure}
Another question which arises is the influence of the wall gradient on the bubble velocity and the
capillary number accordingly. The shear stress controlled by the wall phase gradient changes the
effective velocity near the wall, thus changing the bubble velocity as well.
One can see that if the film thickness is resolved properly the influence of the wall gradient can
be neglected. Fig. \ref{fig:velocities:wall:gradient} shows the center bubble velocity for different
gradients. The average relative error around the mean velocity is $0.1\%$. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/velocities_grad_profiles.eps}
\caption{The center bubble velocity versus the phase gradient. One can neglect the influence of
the wall once the film is properly resolved.
\label{fig:velocities:wall:gradient}
}
\end{figure}

@@

\subsection{The film variation over the bubble}
This section is intended to show the qualitative variation of the film thickness over the bubble.
Though there are simulations for the bubble length simulations for the two-dimensional case, due to
the presentation of data it is hard to extract numerical data. One can see bubble lengths
variations for the two-dimensional simulations for the range of capillary numbers in Fig.
\ref{fig:sehgal:bubble:length}.
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/Bubble/bubble_length.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/Bubble/bubble_sehgal.eps}\\
\caption{The qualitative comparison for the film thickness across
the bubble length. Right (courtesy of \citet{sehgal-microchannel}),
left (present simulations).\label{fig:sehgal:bubble:length}}
\end{figure}
One can see the qualitative agreement, i.e. the thickness increases towards the front meniscus and
rapidly decreases towards the rear meniscus. This shape sometimes is called as a "bullet" shape.
